LCA in R using tidySEM

### 2022-09-04 example_analysis/Daniel_LCA.Rmd
Three LCA models
Fitted 3 LCA models using tidySEM functionality

---
title: "LCA in R"
output: html_notebook
---

USING TIDYSEM:

see functions starting in mx

```{r}
library(tidySEM)
df <- data_mix_ordinal
df[1:4] <- lapply(df, ordered)
mx_lca(data = df,
       classes = 2) -> res
```

```{r}
res$class1
res$latentVars
```

>>>>

---
title: "LCA in R using tidySEM"
output: html_notebook
---

# LOADING THE DATASET

```{r}
library(tidySEM) 
df <- data_mix_ordinal #ask Caspar to rename the dataset in documentation
df[1:4] <- lapply(df, ordered)
```

# 2 class solution

```{r}
# fitting the model
set.seed(123)
mx_lca(data = df, classes = 2) -> res_2_class
```

```{r}
# printing model fit table
print(table_2_class <- tidySEM::table_fit(res_2_class))
```

```{r}
# obtain latent class probabilities
LC_Probabilities_2_class <- tidySEM::class_prob(res_2_class)
print(LC_Probabilities_2_class[1:4])
```
```{r}
# conditional item probabilities
tidySEM::table_prob(res_2_class)
```

# 3 class solution

```{r}
# fitting the model
set.seed(123)
mx_lca(data = df, classes = 3) -> res_3_class
```

```{r}
# printing model fit table
print(table_3_class <- tidySEM::table_fit(res_3_class))
```

```{r}
# obtain latent class probabilities
LC_Probabilities_3_class <- tidySEM::class_prob(res_3_class)
print(LC_Probabilities_3_class[1:4])
```
```{r}
# conditional item probabilities
tidySEM::table_prob(res_3_class)
```

# 4 class solution

```{r}
# fitting the model
set.seed(123)
mx_lca(data = df, classes = 4) -> res_4_class
```

```{r}
# printing model fit table
print(table_4_class <- tidySEM::table_fit(res_4_class))
```

```{r}
# obtain latent class probabilities
LC_Probabilities_4_class <- tidySEM::class_prob(res_4_class)
print(LC_Probabilities_4_class[1:4])
```
```{r}
# conditional item probabilities
tidySEM::table_prob(res_4_class)
```

Comparing model fit

```{r}
print("BIC")
print(c("2 class", table_2_class$BIC)) #lowest
print(c("3 class", table_3_class$BIC))
print(c("4 class", table_4_class$BIC))

print("AIC")
print(c("2 class", table_2_class$AIC))
print(c("3 class", table_3_class$AIC))
print(c("4 class", table_4_class$AIC)) #lowest

print("Entropy")
print(c("2 class", table_2_class$Entropy))
print(c("3 class", table_3_class$Entropy)) #highest
print(c("4 class", table_4_class$Entropy))
```
Using the Bootstrapped Likelihood Ratio Test to compare models

```{r}
tidySEM::BLRT(res_2_class)
```

# APPENDIX
